My Slide Show

### 2024-05-28 Presentation/_fig_creation.qmd
fix slide image displays

@@

varied_train <- c(1, 4) # Specify varied training positions
constant_train <- c(2)     # Specify constant training position
both_test <- c(1, 2, 3, 4)  # Specify test positions
igas_e1 <-  create_plot(varied_train, constant_train, both_test)
igas_e1
ggsave(here::here("Presentation/assets/igas_e1_manip.png"), igas_e1, width = 7.0, height = 6, units = "in", dpi = 400)

@@

create_data <- function(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test) {
    varied_labels <- "Varied-Train"
    constant_labels1 <- "Constant-1-Train"
    constant_labels2 <- "Constant-2-Train"
    constant_labels3 <- "Constant-3-Train"
    constant_labels4 <- "Constant-4-Train"
    constant_labels5 <- "Constant-5-Train"
    constant_labels6 <- "Constant-6-Train"
    test_labels <- "Testing"

    data <- data.frame(
        x = c(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test),
        y = c(rep(0.7, length(varied_train)), rep(1, length(constant_train1)), rep(1.3, length(constant_train2)), 
              rep(1.6, length(constant_train3)), rep(1.9, length(constant_train4)), rep(2.2, length(constant_train5)),
              rep(2.5, length(constant_train6)), rep(0.3, length(both_test))),
        label = c(rep(varied_labels, length(varied_train)),
                  rep(constant_labels1, length(constant_train1)),
                  rep(constant_labels2, length(constant_train2)),
                  rep(constant_labels3, length(constant_train3)),
                  rep(constant_labels4, length(constant_train4)),
                  rep(constant_labels5, length(constant_train5)),
                  rep(constant_labels6, length(constant_train6)),
                  rep(test_labels, length(both_test))),
        color = c(rep("#00A08A", length(varied_train)), rep("#FF0000", length(constant_train1)), rep("#FF0000", length(constant_train2)),
                  rep("#FF0000", length(constant_train3)), rep("#FF0000", length(constant_train4)), rep("#FF0000", length(constant_train5)),
                  rep("#FF0000", length(constant_train6)), rep("#ECCBAE", length(both_test)))
    )

@@

create_plot <- function(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test) {
    data <- create_data(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test)
    segments <- create_segments(data)

@@

    ggplot() +
        geom_segment(data = segments, aes(x = x, xend = xend, y = y, yend = yend),
                     linewidth = 1.2, color = "gray40") +
        geom_point(data = data, aes(x = x, y = y, color = color), size = 12) +
        geom_text(data = data, aes(x = x, y = y, label = label),
                  color = "black", size = 4, vjust = -1.8, hjust = 0.5, fontface = "italic") +
        geom_segment(aes(x = train_x - 0.3, xend = train_x - 0.3, y = train_y_start, yend = train_y_end), color = "black", linewidth = 1.2) +
        geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_end, yend = train_y_end), color = "black", linewidth = 1.2) +
        geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_start, yend = train_y_start), color = "black", linewidth = 1.2) +
        geom_text(aes(x = train_x - .6, y = train_text_y, label = "Training"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4, fontface = "bold") +
        geom_segment(aes(x = test_x - 0.3, xend = test_x - 0.3, y = test_y_start, yend = test_y_end), color = "black", linewidth = 1.2) +
        geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_end, yend = test_y_end), color = "black", linewidth = 1.2) +
        geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_start, yend = test_y_start), color = "black", linewidth = 1.2) +
        geom_text(aes(x = test_x - .65, y = test_text_y, label = "Testing"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4, fontface = "bold") +
        scale_color_identity() +
        xlim(min(data$x) - 2, max(data$x) + 1) +
        ylim(0, 3.0) +
        theme_void() +
        theme(legend.position = "none",
              plot.margin = margin(10, 20, 10, 20),
              plot.background = element_rect(fill = "white", color = NA),
              panel.background = element_rect(fill = "white", color = NA))
}

# Example usage
varied_train <- c(3, 5)                   # Specify varied training positions
constant_train1 <- c(1)                   # Specify constant training position for group 1
constant_train2 <- c(2)                   # Specify constant training position for group 2
constant_train3 <- c(3)                   # Specify constant training position for group 3
constant_train4 <- c(4)                   # Specify constant training position for group 4
constant_train5 <- c(5) # Specify constant training position for group 5
constant_train6 <- c(6) # Specify constant training position for group 6
both_test <- c(1, 2, 3, 4, 5, 6) # Specify test positions
igas_e2 <- create_plot(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test)
igas_e2

ggsave(here::here("Presentation/assets/igas_e2_manip.png"), igas_e2, width = 7.5, height = 8, units = "in", dpi = 600)

>>>>

```{r}
pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,stringr, here,conflicted, gt, ggh4x, patchwork, knitr)
walk(c("Display_Functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))

@@

varied_train <- c(1, 4) # Specify varied training positions
constant_train <- c(2)     # Specify constant training position
both_test <- c(1, 2, 3, 4)  # Specify test positions
igas_e1 <-  create_plot(varied_train, constant_train, both_test)
igas_e1
ggsave(here::here("Presentation/assets/igas_e1_manip.png"), igas_e1, width = 9.0, height = 6, units = "in", dpi = 300)

create_data <- function(varied_train, constant_train, both_test, test_labels_bottom) {
  varied_labels <- "Varied-Train"
  constant_labels <- "Constant-Train"
  test_labels <- "Testing"

  data <- data.frame(
    x = c(varied_train, constant_train, both_test),
    y = c(rep(0.7, length(varied_train)), rep(1, length(constant_train)), rep(0.3, length(both_test))),
    label = c(rep(varied_labels, length(varied_train)),
              rep(constant_labels, length(constant_train)),
              rep(test_labels, length(both_test))),
    color = c(rep("#00A08A", length(varied_train)), rep("#FF0000", length(constant_train)), rep("#ECCBAE", length(both_test))),
    label_bottom = c(rep(NA, length(varied_train) + length(constant_train)), test_labels_bottom)
  )

create_plot <- function(varied_train, constant_train, both_test, test_labels_bottom) {
  data <- create_data(varied_train, constant_train, both_test, test_labels_bottom)
  segments <- create_segments(data)

  ggplot() +
    geom_segment(data = segments, aes(x = x, xend = xend, y = y, yend = yend),
                 linewidth = 1.2, color = "gray40") +
    geom_point(data = data, aes(x = x, y = y, color = color), size = 12) +
    geom_text(data = data, aes(x = x, y = y+.01, label = label),
              color = "black", size = 4, vjust = -1.8, hjust = 0.5, fontface = "italic") +
    geom_text(data = data, aes(x = x, y = 0.2, label = label_bottom),
              color = "black", size = 4, vjust = 1.8, hjust = 0.5, fontface = "italic") +
    geom_segment(aes(x = train_x - 0.3, xend = train_x - 0.3, y = train_y_start, yend = train_y_end), color = "black", linewidth = 1.2) +
    geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_end, yend = train_y_end), color = "black", linewidth = 1.2) +
    geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_start, yend = train_y_start), color = "black", linewidth = 1.2) +
    geom_text(aes(x = train_x - .6, y = train_text_y, label = "Training"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4, fontface = "bold") +
    geom_segment(aes(x = test_x - 0.3, xend = test_x - 0.3, y = test_y_start, yend = test_y_end), color = "black", linewidth = 1.2) +
    geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_end, yend = test_y_end), color = "black", linewidth = 1.2) +
    geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_start, yend = test_y_start), color = "black", linewidth = 1.2) +
    geom_text(aes(x = test_x - .6, y = test_text_y, label = "Testing"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4, fontface = "bold") +
    scale_color_manual(values = c("#00A08A","#ECCBAE", "#FF0000")) +
    xlim(min(data$x) - 2, max(data$x) + 1) +
    ylim(0, 1.5) +
    theme_void() +
    theme(
          # plot.margin = margin(10, 20, 10, 20),
          # plot.background = element_rect(fill = "white", color = NA),
          # panel.background = element_rect(fill = "white", color = NA), 
          legend.position = "none",)
}

varied_train <- c(4, 5, 6) # Specify varied training positions
constant_train <- c(4)     # Specify constant training position
both_test <- c(1, 2, 3, 4, 5, 6)  # Specify test positions
test_labels_bottom <- c("100-350", "350-550", "600-800", "800-1000", "1000-1200", "1200-1400") # Labels for bottom of test points
htw_e1 <- create_plot(varied_train, constant_train, both_test, test_labels_bottom)
htw_e1

varied_train <- c(1, 2, 3) # Specify varied training positions
constant_train <- c(3)     # Specify constant training position
both_test <- c(1, 2, 3, 4, 5, 6)  # Specify test positions
htw_e2 <- create_plot(varied_train, constant_train, both_test,test_labels_bottom)
htw_e2

varied_train <- c(1, 4) # Specify varied training positions
constant_train <- c(2)     # Specify constant training position
both_test <- c(1, 2, 3, 4)  # Specify test positions
test_labels_bottom <- c("610", "760", "835", "910") # Labels for bottom of test points
igas_e1 <-  create_plot(varied_train, constant_train, both_test,test_labels_bottom)
igas_e1
ggsave(here::here("Presentation/assets/igas_e1_manip.png"), igas_e1, width = 9.0, height = 6, units = "in", dpi = 300)

@@

create_data <- function(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test,test_labels_bottom) {
    varied_labels <- "Varied-Train"
    constant_labels1 <- "Constant-1-Train"
    constant_labels2 <- "Constant-2-Train"
    constant_labels3 <- "Constant-3-Train"
    constant_labels4 <- "Constant-4-Train"
    constant_labels5 <- "Constant-5-Train"
    constant_labels6 <- "Constant-6-Train"
    test_labels <- "Testing"

    data <- data.frame(
        x = c(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test),
        y = c(rep(0.7, length(varied_train)), rep(1, length(constant_train1)), rep(1.3, length(constant_train2)), 
              rep(1.6, length(constant_train3)), rep(1.9, length(constant_train4)), rep(2.2, length(constant_train5)),
              rep(2.5, length(constant_train6)), rep(0.3, length(both_test))),
        label = c(rep(varied_labels, length(varied_train)),
                  rep(constant_labels1, length(constant_train1)),
                  rep(constant_labels2, length(constant_train2)),
                  rep(constant_labels3, length(constant_train3)),
                  rep(constant_labels4, length(constant_train4)),
                  rep(constant_labels5, length(constant_train5)),
                  rep(constant_labels6, length(constant_train6)),
                  rep(test_labels, length(both_test))),
        color = c(rep("#00A08A", length(varied_train)), rep("#FF0000", length(constant_train1)), rep("#FF0000", length(constant_train2)),
                  rep("#FF0000", length(constant_train3)), rep("#FF0000", length(constant_train4)), rep("#FF0000", length(constant_train5)),
                  rep("#FF0000", length(constant_train6)), rep("#ECCBAE", length(both_test))),
        label_bottom = c(rep(NA, length(varied_train) + length(constant_train)*6), test_labels_bottom)
    )

@@

create_plot <- function(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test,test_labels_bottom) {
    data <- create_data(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test,test_labels_bottom)
    segments <- create_segments(data)

@@

    ggplot() +
        geom_segment(data = segments, aes(x = x, xend = xend, y = y, yend = yend),
                     linewidth = 1.2, color = "gray40") +
        geom_point(data = data, aes(x = x, y = y, color = color), size = 12) +
        geom_text(data = data, aes(x = x, y = y, label = label),
                  color = "black", size = 4, vjust = -1.8, hjust = 0.5, fontface = "italic") +
      geom_text(data = data, aes(x = x, y = 0.2, label = label_bottom),
              color = "black", size = 4, vjust = 1.8, hjust = 0.5, fontface = "italic") +
        geom_segment(aes(x = train_x - 0.3, xend = train_x - 0.3, y = train_y_start, yend = train_y_end), color = "black", linewidth = 1.2) +
        geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_end, yend = train_y_end), color = "black", linewidth = 1.2) +
        geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_start, yend = train_y_start), color = "black", linewidth = 1.2) +
        geom_text(aes(x = train_x - .6, y = train_text_y, label = "Training"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4, fontface = "bold") +
        geom_segment(aes(x = test_x - 0.3, xend = test_x - 0.3, y = test_y_start, yend = test_y_end), color = "black", linewidth = 1.2) +
        geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_end, yend = test_y_end), color = "black", linewidth = 1.2) +
        geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_start, yend = test_y_start), color = "black", linewidth = 1.2) +
        geom_text(aes(x = test_x - .65, y = test_text_y, label = "Testing"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4, fontface = "bold") +
        scale_color_identity() +
        xlim(min(data$x) - 2, max(data$x) + 1) +
        ylim(0, 3.0) +
        theme_void() +
        theme(legend.position = "none")
}

# Example usage
varied_train <- c(3, 5)                   # Specify varied training positions
constant_train1 <- c(1)                   # Specify constant training position for group 1
constant_train2 <- c(2)                   # Specify constant training position for group 2
constant_train3 <- c(3)                   # Specify constant training position for group 3
constant_train4 <- c(4)                   # Specify constant training position for group 4
constant_train5 <- c(5) # Specify constant training position for group 5
constant_train6 <- c(6) # Specify constant training position for group 6
both_test <- c(1, 2, 3, 4, 5, 6) # Specify test positions
test_labels_bottom <- c("400", "500", "625","675", "800", "900")
igas_e2 <- create_plot(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test,test_labels_bottom)
igas_e2

ggsave(here::here("Presentation/assets/igas_e2_manip.png"), igas_e2, width = 9, height = 6, units = "in", dpi = 300)

### 2024-05-28 Presentation/_hold_slides.qmd
fix slide image displays

---
title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
page-layout: full
aliases:
  - /slides.html
css: /Assets/Style/slides.css
format-links: [clean-revealjs, pptx,gfm]
format: 
  html: 
    subtitle: "Dissertation Defense"
  clean-revealjs:
    #theme: moon #white
    #output-ext: revealjs.html
    # template-partials:
    #   - assets/title-slide.html
    output-file: slides_revealjs
    date: 05/28/204
    slideNumber: true
    hash-type: number # Use slide numbers in the URL hash
    center: true
    scrollable: true
    chalkboard:
      theme: whiteboard
  pptx:
    incremental: false
  hugo-md:
    include: false
    html-math-method: mathjax
    output-file: slides_hugo.md
  gfm:
    output: false
    output-file: slides_gfm.md
author:
  - name: Thomas Gorman
    url: https://tegorman13.github.io
    orcid: 0000-0001-5366-5442
    affiliations:
      - name: Indiana University
        department: Psychological & Brain Sciences, Cognitive Science
# params:
#   start_slide: 
#engine: knitr
---

{{< include /Presentation/embed_slides.qmd >}}

# Learning Generalization

- Learning is often specific
- Longstanding scientific interest in how to improve generalization or transfer

------------------------------------------------------------------------

## Variability

- Variation during training linked to improved transfer in numerous domains 
- What does "variability mean in the context of learning interventions?"

## Types of Variability

- The number of unique items/problems experienced
- How spread out examples are

## My Dissertation Focus

- Number of unique examples
- Visuomotor skill learning and function learning

- Addressing methodological shortcomings of previous work
- Adapting cognitive models from other domains to account for results

------------------------------------------------------------------------

## Common Experimental Manipulations

- Varied vs. Constant

## Common Empirical Patterns

:::::::::  columns
::: {.column width="55%"}
### Training
- Both training conditions complete the same number of training trials.
- Varied group has worse training performance.

![](assets/train_pattern.png)
:::

::: {.column width="45%"} 
::: {.fragment}
### Testing

- Tested from novel conditions.
- Varied group has better test performance

![](assets/test_pattern.png)
:::
:::
:::::::::

------------------------------------------------------------------------

## But also plenty of contradictory results and complications

- Cases where varied training doesn't benefit generalization
- Cases where more training variation results in worse outcomes
- Cases where the influence of variation interacts with some other factor
    - difficulty
    - prior knowledge
    - Frequency effects, or amount of training/learning before testing

------------------------------------------------------------------------

## Theoretical Frameworks

-   Schema Theory (Schmidt, 1975)
-   Desirable Difficulties Framework (Bjork & Bjork, 2011)
-   Challenge Point Framework (Guadagnoli & Lee, 2004)

::: footer
@schmidtSchemaTheoryDiscrete1975 @bjorkMakingThingsHard2011 @guadagnoliChallengePointFramework2004
:::

<!-- ![](assets/fig-toy-model1-1-1.png) -->

------------------------------------------------------------------------

## Overview of Current Work

### Project 1[^1]

- Visuomotor projectile launching task
- two experiments
- Beneficial effect of variability
- Instance-based similarity model

### Project 2

- Visuomotor extrapolation task
- Three experiments
- Effect of variability is null or negative
- Connectionist model (ALM) and hybrid associative & rule model (EXAM)

::: footer
[^1]: Now published in Cognitive Psychology @gormanInstancebasedModelAccount2022
:::
--

# Project 1  - Issues with previous research

- Assumptions about what is encoded
- Assumptions about the formation of abstractions 
- Aggregation issues and similarity confounds

---

## designs that seemingly overcome these issues

- Kerr & Booth 1978

::: footer
@kerrSpecificVariedPractice1978
:::

## Experiment 1

- Conceptual replication of Kerr & Booth design 
- Testing classic pattern as well

------------------------------------------------------------------------

## Hit The Target Task

:::::: column-page-right
::::: {.columns}
:::: {.column width="60%"}

::: {.content-visible when-format="html"}
![](assets/htt_vid.mov){height="540" loop="true" autoplay="true" style="max-width: 100%"}
:::

::: {.content-visible unless-format="html"}
![](assets/methodsFig1.png)
:::

@@

:::: {.column width="40%"}
- **Training Stage** - 200 training trials with feedback. Constant groups trains from single position. Varied group practices from two positions. 
- **Transfer Stage** - All subjects tested from both positions they were trained, and the positions trained by other group
- **Data recorded** - For every throw, recorded the X velocity and Y velocity of ball at release
::::

:::::
::::::

------------------------------------------------------------------------

## Project 1 - Manipulations  {.smaller}

:::: {.columns}
::: {.column width="50%"}

### Experiment 1
- Train varied group from 2 positions, and a constant group from 1.
- Test both groups from the trained positions - and 1 novel position

![](assets/igas_e1_manip.png)

::: {.column width="50%"}
### Experiment 2
- 6 distinct constant conditions

![](assets/igas_e2_manip.png)
:::

------------------------------------------------------------------------

## Project 1 - Experiment 1 Results

:::: {.columns}
::: {.column width="40%"}
### Experiment 1
![](assets/igas_e1_manip.png)
:::
::: {.column width="60%"}
::: fragment
### Training
![](assets/htt_e1_train.png)
:::
::: fragment
### Testing
![](assets/fig-IGAS_Testing1-1-2.png)
:::
:::
::::

## Project 1 - Experiment 2 Results

:::: {.columns}
::: {.column width="40%"}
### Experiment 1
![](assets/igas_e2_manip.png)
:::
::: {.column width="60%"}
::: fragment
### Training
![](assets/htt_e2_train.png)
:::
::: fragment
### Testing
![](assets/htt_e2_test.png)
:::
:::
::::

------------------------------------------------------------------------

## Project 1 - Discussion

-   Varied training group's superior performance
-   Computational modeling results with IGAS
-   Theoretical implications

------------------------------------------------------------------------

:::: {.columns}
::: {.column width="50%"}

![](assets/sol_space2.png){width="65%"}
![](assets/full_space2.png){width="50%"}
:::

::: {.column width="50%"}

- $d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 }$
- $Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}})$

:::
::::

:::: {.columns}
::: {.column width="70%"}

![](assets/sol_space.png)

![](assets/full_space.png)
:::
::: {.column width="30%"}
### Model Steps

@@

## Computational Model - Does Similarity Account for Effect of Variability?

- Test whether similarity explains the difference in performance between Constant and Varied conditions
  - Assuming equivalent generalization (1 c for both groups) - similarity improves model fit, but does not explain group difference
  - Assume training condition influences generalization gradient (fit c separately) - now similarity does explain the difference between Constant and Varied.

::: footer
**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}}) $$
**Equation 2:** $$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
:::

## Project 1 General Discussion {.smaller .r-fit-text}

------------------------------------------------------------------------

# Project 2 - Variability and Extrapolation in a Function Learning Task

-   Influence of varied practice in a function learning task
-   Experiments 1, 2, and 3:
    -   Training regimes and testing conditions
    -   Learning, discrimination, and extrapolation performance metrics

------------------------------------------------------------------------

## Project 2 - Questions and Goals

**Empirical**
- Design a task-space large enough to assess multiple degrees of extrapolation 
- Compare varied and constant generalization from several distinct distances from their nearest training condition

**Model-based**
- If variation does influence extrapolation, can an associative learning model with similarity-based activation provide a good account?
- Can our modelling framework simultaneously account for both training and testing data?
- Accounting for the full distribution of responses

------------------------------------------------------------------------

## Hit The Wall Task

<!-- {{< video assets/htw_vid.mov width="720" height="540" >}} -->

::: {.content-visible when-format="html"}
![](assets/htw_vid.mov){height="400" loop="true" autoplay="true"}
:::

::: {.content-visible unless-format="html"}
![](assets/htw_task_fig.png)
:::

- Target velocity presented at top of screen
- Participants attempt to "hit the wall" at the correct velocity
- Feedback during training - how many units above or below the target-band
- Only the "x velocity" component of the throw is relevant to the task

------------------------------------------------------------------------

## Project 2 - Experiment 1 Design {.nostretch .smaller}

:::: {.columns}
::: {.column width="60%"}
![](assets/htw_e1_manip.png){fig-align="left" fig-align="top" width="65%"}

![](assets/e1_design.png){fig-align="left" fig-align="top" width="70%"}
:::
::: {.column width="40%"}

- 156 participants included in final analysis
- Varied group trains from 3 "velocity bands", constant group from 1
:::
::::

------------------------------------------------------------------------

## Project 2 - Experiment 1 Results {.nostretch}

::: {.columns}
::: {.column width="50%"}
![Plot 1](assets/htw_e1_test1.png)
![Plot 3](assets/htw_e1_test3.png)
:::

::: {.column width="50%"}
![Plot 2](assets/htw_e1_test2.png)
![Plot 4](assets/htw_e1_test4.png)
:::
:::

## Project 2 - Experiment 2 Design {.smaller}

:::: {.columns}
::: {.column width="60%"}
![](assets/htw_e2_manip.png){fig-align="left" fig-align="top"}

![](assets/e2_design.png){fig-align="left" fig-align="top"}
:::
::: {.column width="40%"}

<br><br><br><br>

- Training and Testing bands are in reversed order, relative to Experiment 1
- 110 participants included in final analysis

:::
::::

## Project 2 - Experiment 2 Results {.nostretch}

::: {.columns}
::: {.column width="50%"}
![Plot 1](assets/htw_e2_test1.png)
![Plot 3](assets/htw_e2_test3.png)
:::

::: {.column width="50%"}
![Plot 2](assets/htw_e2_test2.png)
![Plot 4](assets/htw_e2_test4.png)
:::
:::

## Project 2 - Experiment 3

- Ordinal Feedback
  - directional feedback indicating too high, too low, or correct
- Both Original (Experiment 1), and reverse (Experiment 2) orders included
- 195 participants included in final analysis

## Project 2 - Experiment 3 Results {.nostretch}

## Accuracy

:::: {.columns}

::: {.column width="50%"}
![Plot 1](assets/htw_e3_test1.png)
:::

::: {.column width="50%"}
![Plot 3](assets/htw_e3_test2.png)
:::

## Discrimination

:::: {.columns}

::: {.column width="50%"}
![Plot 1](assets/htw_e3_test3.png)
:::

::: {.column width="50%"}
![Plot 3](assets/htw_e3_test4.png)
:::

------------------------------------------------------------------------

# Project 2 - Computational Modeling

## Project 2 - ALM

![](assets/fig-alm-diagram-1-1.png)

------------------------------------------------------------------------

## ALM

|                    | **ALM Response Generation**                                        |                                                                                               |
|------------------|-----------------------------|-------------------------|
| Input Activation   | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$    | Input nodes activate as a function of Gaussian similarity to stimulus                         |
| Output Activation  | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$                        | Output unit $O_j$ activation is the weighted sum of input activations and association weights |
| Output Probability | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$                    | The response, $Y_j$ probabilites computed via Luce's choice rule                              |
| Mean Output        | $m(X) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$ | Weighted average of probabilities determines response to X                                    |
|                    | **ALM Learning**                                                   |                                                                                               |
| Feedback           | $f_j(Z) = e^{-c(Z-Y_j)^2}$                                         | feedback signal Z computed as similarity between ideal response and observed response         |
| magnitude of error | $\Delta_{ji}=(f_{j}(Z)-o_{j}(X))a_{i}(X)$                          | Delta rule to update weights.                                                                 |
| Update Weights     | $w_{ji}^{new}=w_{ji}+\eta\Delta_{ji}$                              | Updates scaled by learning rate parameter $\eta$.                                             |

------------------------------------------------------------------------

## EXAM

|                    | **EXAM Response Generation**                                                                                     |                                                                                                               |
|--------------------|-----------------------------------------------------------------------------------------------------------------|---------------------------------------------------------------------------------------------------------------|
| Instance Retrieval | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$                                                                 | Novel test stimulus $X$ activates input nodes $X_i$                                                           |
| Slope Computation  | $S = \frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}$                                                                     | Slope value, $S$ computed from nearest training instances                                                     |
| Response           | $E[Y|X_i] = m(X_i) + S \cdot [X - X_i]$                                                                         | Final EXAM response is the ALM response for the nearest training stimulus, $m(X_i)$, adjusted by local slope $S$. |

------------------------------------------------------------------------

## Project 2 - Model Fitting Procedure {.r-fit-text}

### Approximate Bayesian Computation

:::: {.columns}

::: {.column width="60%"}
![](assets/abc_diagram1.png)
:::

- simulation based approach
- approximate likelihood
- uncertainty in parameter values
- full distribution of plausible model predictions for each participant

## Modelling Results

![](assets/fig-ee-e1-1.png)

# General Discussion

-   Compare HTT and HTW
-   Empirical findings summary
-   Computational modeling contributions

------------------------------------------------------------------------

## Comparison {.smaller .r-fit-text}

| Dimension | HTT (Project 1) | HTW (Project 2) |
|----------------|--------------------------------|-------------------------|
| Task Description | Projectile launching to hit a target | Projectile launching to hit wall at a specific velocity |
| Task Complexity | More complex parabolic trajectory, both x and y velocities relevant to outcome | Simpler 1D mapping of force to outcome. Only x velocity is relevant. |
| Task Space | More complex: xy velocity combinations closer to the solution space may still result in worse feedback due to striking the barrier. | Simpler: smooth, linear mapping between velocity and feedback. |
| Perceptual salience of Varied Conditions | Varied conditions (# of throwing distances) are perceptually distinct, i.e. salient differences in distance between launching box and target. | Varied conditions (# of velocity bands) are less salient - only difference is the numeral displayed on screen. |
| Testing Feedback | Testing always included feedback | Primary testing stage had no feedback. |
| Potential for Learning during Testing | Limited potential for learning during testing due to feedback. | Some potential for learning during no-feedback testing by observing ball trajectory. |
| Training Experience | Varied group gets half as much experience on any one position as the constant group. | Varied group gets 1/3 as much experience on any one velocity band as the constant group. |
| Testing Structure | Random interleaving of trained/transfer testing distances. | Blocked structure, separately testing trained vs extrapolation testing bands. |

------------------------------------------------------------------------

## Conclusion

## References
::: {#refs}
:::

::: {.content-visible when-format="html"}
## Manuscript {.scrollable .unnumbered .unlisted}

```{=html}
<iframe width="800" height="750" src="https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html" title="Webpage example"></iframe>
```
:::

------------------------------------------------------------------------

>>>>

---
title: My Slide Show
format:
  revealjs: default
---

## Project 1 - Design  {.nostretch .smaller}

:::: {.columns}
::: {.column width="40%"}

### Experiment 1222
- Train varied group from 2 positions, and a constant group from 1.
- Test both groups from the trained positions - and 1 novel position

![](assets/igas_e1_manip.png){.absolute bottom=30 width="50%"}

::: {.column width="60%"}
### Experiment 2

- 6 distinct constant conditions

![](assets/igas_e2_manip.png){.absolute bottom=0 width="90%"}
:::

@@

@@
